### 2016-04-28 paper/paper.tex
hmm
¯\_(ツ)_/¯
add peercoin/proof-of-stake background

@@

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to solve local challenges rather than remote ones, leading to the
proof-of-work being a computational puzzle, rather than one based on
participation in a network denial of service. Thus, DDoSCoin must have a way to
agree on what victims are acceptable targets for the proofs to be considered
valid.

@@

\subsection{Ethical Considerations}
¯\\\_(ツ)\_/¯

Днепр kůň dominī Ngữ

>>>>

\subsection{Proof-of-Stake}

Proof-of-Stake is an alternate way of generating new blocks in a cryptocurrency.
In this system, blocks are ``minted'' (rather than mined) based on how much
stake the miner has in the currency (rather than their fraction of computational
power). Proof-of-stake assumes that the underlying cryptocurrency is already
somewhat distributed, for example through the use of a traditional proof-of-work
system. In this subsection, we will describe Peercoin, a currently active
alternate cryptocurrency that employs a hybrid proof-of-work and proof-of-stake
algorithm to mint blocks.

Peercoin's proof-of-stake allows currency holders to mint new blocks based on
how many coin-days they are able and willing to consume. ``Coin-days
consumed'' is a measure of the product of the amount of coins spent, and the
number of days the have not been previously spent. For example, to consume 10
coin-days, a currency holder can spend 10 Peercoin that they have held for a
day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
that the holder can send these coins to anyone (including themselves) in order
to consume the coin age.

To mint a new block, a minter creates a special transaction (presumably one
where the minter pays themself) where one of the
inputs has been unspent for at least 30 days. The resulting transaction, along
with a timestamp, must meet a certain hash target that gets easier proportional to how many
coin-days are consumed. For example, if the current difficulty gives a minter
consuming 100 coin-days a 1\% chance of minting a block per second, a minter
that was able to consume 200 coin-days would have a 2\% chance per second.

The input to the hash includes information about the ``aged'' transaction, as
well as a current timestamp\footnote{In recent versions of Peercoin, the hash
also includes a stakeModifier which is computed from recent blocks; however,
these details are not important for our purposes}. If this hash is less than the
current target multiplied by the number of coin-days consumed in the
transaction, then the transaction meets the proof-of-stake difficulty and a new
block is minted. Although this looks similar to a proof-of-work check where a
hash is being compared to a target, here the only varying inputs are the
long-lived (aged) input transaction, and a corse-grained timestamp with a
resolution of 1 second. Thus, for each aged unspent transaction output they
control, minters perform only one hash per second in order to solve the
proof-of-stake.

% hash(nStakeModifier + txPrev.block.nTime + txPrev.offset + txPrev.nTime +
%       txPrev.vout.n + nTime) < bnTarget * nCoinDayWeight
%
% ss << nTimeBlockFrom << nTxPrevOffset << txPrev.nTime << prevout.n <<
%   nTimeTx;
% given a new tx that is going to be my "proof-of-stake" tx,
% which has an input from prevTx (where prevTx is at least 30 days old)
% H(nStakeModifier + txPrev.block.nTime + txPrev.offset + txPrev.nTime +
%   txPrev.vout.n + tx.nTime)

% stakeModifiers (in v0.3): you start from the block where txPrev was in,
% and then walk forward until the first block that was made more than
% GetStakeModifierSelectionInterval() seconds after that the block txPrev was in (about 8.8 days...)
% If that block has the stakeModifier flag set, use its stakeModifier

% Ist das system relevant?
In Peercoin, coins cannot age beyond 90-days; coins that have not been consumed
after 90-days are counted as 90-day-old coins. This prevents very old
coin-holders from being able to disrupt the blockchain at a future date,
potentially causing a large fork of the blockchain and destabalizing it.

When a proof-of-stake is minted, the minter is allowed to collect a small
subsidy proportional to the coin-age consumed in their proof-of-stake
transaction. This serves as the only reward for a minter, as transaction fees are not
collected by minters in Peercoin.

@@

If DDoSCoin accepted proofs against any TLS 1.2 server, miners would be
incentivized to solve local challenges rather than remote ones, leading to the
proof-of-work being a computational puzzle, rather than one based on
participation in a network denial of service. Thus, DDoSCoin must have a way to
agree on what victims are acceptable targets for the proofs-of-work to be considered
valid.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
\shrug

% ¯\_(ツ)_/¯
